Supplmental Information : Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes

### 2017-10-09 Ben_Manuscripts/structure_paper/results.tex
Rethinking the scope of the paper. Renamed folders to be more descriptive

The initial distance between layers can influence the approach towards
equilibrium. In the real system, according to wide angle X-ray
scattering (WAXS) experiments, layers are stacked 3.7 \angstrom apart.
A characteristic of equilibrated systems simulated in this way, is a
defined, cylindrical and open pore structure. Benzene rings arrange in
a helical conformation after equilbration. The membrane is about 8 nm
thick. We will refer to this system as Phase A. (Fig ~\ref{fig:phaseA})
Simulations of systems built with layers stacked > 4 \angstrom apart
results in a pore structure characterized by high radial disorder,
while maintaining partitioning between hydrophobic and hydrophilic
regions. This will be called phase B (Fig~\ref{fig:phaseB})
% The arrangement of sodium ions (which are closely bound to carbonyl
% head groups) can be well-approximated by a gaussian distribution 
It is apparent that this LLC membrane may exist in at least two
metastable states. The distinct difference in pore structure exhibited
by each phase will likely lead to different transport mechanisms.
Understanding which phase exists experimentally is necessary in order
to appropriately study the system.
%Like phase A, phase B can form at 280K. 
%The phase is also present when phase A is heated close to its isotropic transition point
%There are distinct differences in the membrane and pore structures between each state (Fig~\ref{fig:porestructures})

% Paragraph describing the experimental 2D WAXS Pattern
The experimental 2D WAXS measurement contains five major reflections which
our model intends to reproduce (Fig ~\ref{fig:WAXSexp}). The first is located
at qz = 1.7 \angstrom \textsuperscript{-1}, corresponding to a real space 
spacing of 3.7 \angstrom. The reflection is attributed to pi-pi stacking
between aromatic rings in the direction perpendicular to the membrane plane, or z-axis. 
For simplicity, this reflection will be referred to as R-pi. A weak intensity
line is located at exactly half the qz value of R-pi (qz = 0.85 \angstrom \textsuperscript{-1}), corresponding to a 
real space periodic spacing of 7.4 \angstroms. This reflection has been 
attributed to 2\textsubscript{1} helical ordering of aromatic rings along the
z axis and will therefore be referred to as R-helix. If positions of the 
aromatic rings can be traced by a helix, then for each turn in the helix, 
there should be two aromatic rings. A third major reflection is marked by 
a low intensity ring located at r = 1.4 \angstrom \textsuperscript{-1}. The
real space separation corresponds to 4.5 \angstroms which is characteristic
of the average spacing between packed alkane chains. This reflection will be
called R-alkanes. Within R-alkanes, are four spots of higher intensity which 
will be called R-spots. All are located \approx 40 degrees from the qz axis
in their respective quadrants. In many liquid crystal systems this can be
attributed to the tilt angle of the alkane chains with respect to the xy axis. 
The final major reflections correspond to the spacing and symmetry of the d100 
plane which can be related to the distance between pores. The feature is
characterized by dots along qz = 0. The spacing between dots is indicative
of the hexagonal symmetry of the packed pores. It is easiest to interpret 
the data by radially integrating the 2D data to get a 1D curve which has
also been done.

Full comparison of experimental 2D WAXS with simulated X-ray diffraction patterns produced from MD trajectories shows the most consistency with the parallel-displaced configuration made up of 5 monomers per layer.
        \begin{itemize}
                \item Phase A
                \begin{itemize}
                        \item Purely stacked configuration is missing reflections at 2, 4, 8 and 10 0'clock, but they are there in the parallel displaced conformation
                        \item There is evidence that the stacked configuration will shift towards an offset configuration over time. WAXS spots show up after short simulations, in which case there is visible movement away from a perfectly stacked, towards a parallel displaced conformation
                        \item Pi-stacking reflections are present in all cases but at spacings higher than shown experimentally. This is not surprising since GAFF will not properly treat pi-stacking.
                        \item Interestingly, the spots, which are usually associated with alkyl chain tilt, still appear with an average tilt angle of 0 degrees
                \end{itemize}
                \item Phase B
                \begin{itemize}
                        \item Stacking refelctions present indicating separation of $\approx$ 5 \angstrom
                        \item No spots at all which is consistent with the disorder shown by the rings in the pore
                \end{itemize}
                \item Both phases show a ring in the simulated 2D WAXS patterns at q $\approx$ 1.4 \angstrom \textsuperscript{-1} which is typical of packed alkane chains
                \item Both phases exhibit axial reflections. Even though the rings are not ordered in phase B,
%MRS2: not quite clear what physical structures the axial reflections correspond to (what are the distances? What do they correspond to?)
they are still partitioned into layers which gives rise to an axial refelction at the same distance where we expect alkane chain packing to be present
%MRS2: how are they layers defined here? Can you bring in more information about the nonuniformity of the density?
%BJC2: Are you thinking about the fourier transforms? I could bring that in
        \end{itemize}

>>>>

The initial distance between layers can influence the approach towards
equilibrium. In the real system, according to wide angle X-ray
scattering (WAXS) experiments, layers are stacked 3.7 \angstrom apart.
A characteristic of equilibrated systems set up in this way, is a
defined, cylindrical and open pore structure. Benzene rings arrange in
a helical conformation after equilbration. We will refer to this system
as Basin A (Fig ~\ref{fig:phaseA}). Simulations of systems built with
layers stacked > 4 \angstrom apart results in a pore structure 
characterized by high radial disorder, while maintaining partitioning 
between hydrophobic and hydrophilic regions. This will be called Basin
B (Fig~\ref{fig:phaseB}).
% The arrangement of sodium ions (which are closely bound to carbonyl
% head groups) can be well-approximated by a gaussian distribution 
It is apparent that this LLC membrane may exist in at least two
metastable states. The distinct difference in pore structure exhibited
by each phase will likely lead to different transport mechanisms.
Understanding which phase exists experimentally is necessary in order
to appropriately study the system.
% Like Basin A, Basin B can form at 280K. 
% The phase is also present when phase A is heated close to its isotropic transition point
% There are distinct differences in the membrane and pore structures between each state (Fig~\ref{fig:porestructures})

% Paragraph describing the experimental 2D WAXS Pattern
The experimental 2D WAXS measurement contains five major reflections which
our model intends to reproduce (Fig ~\ref{fig:WAXSexp}). The first is located
at qz = 1.7 \angstrom \textsuperscript{-1}, corresponding to a real space 
spacing of 3.7 \angstrom. The reflection is attributed to pi-pi stacking
between aromatic rings in the direction perpendicular to the membrane plane, or z-axis. 
For simplicity, this reflection will be referred to as R-pi. A weak intensity
line is located at exactly half the qz value of R-pi (qz = 0.85 \angstrom 
\textsuperscript{-1}), corresponding to a real space periodic spacing of 
7.4 \angstroms. This reflection has been attributed to 2\textsubscript{1}
helical ordering of aromatic rings along the z axis and will therefore be
referred to as R-helix. If positions of the aromatic rings can be traced
by a helix, then for each turn in the helix, there should be two aromatic 
rings. A third major reflection is marked by a low intensity ring located
at r = 1.4 \angstrom \textsuperscript{-1}. The real space separation 
corresponds to 4.5 \angstroms which is characteristic of the average spacing
between packed alkane chains. This reflection will be called R-alkanes. 
Within R-alkanes, are four spots of higher intensity which will be called
R-spots. All are located \approx 40 degrees from the qz axis
in their respective quadrants. In many liquid crystal systems this can be
attributed to the tilt angle of the alkane chains with respect to the xy plane. 
The final major reflections correspond to the spacing and symmetry of the d100 
plane which can be related to the distance between pores. The feature is
characterized by dots along qz = 0. The spacing between dots is indicative
of the hexagonal symmetry of the packed pores. It is easiest to interpret 
the data by radially integrating the 2D data to get a 1D curve which has
also been done.

Full comparison of experimental 2D WAXS with simulated X-ray diffraction patterns produced from MD trajectories shows the most consistency with the parallel-displaced configuration made up of 5 monomers per layer.
        \begin{itemize}
                \item Basin A
                \begin{itemize}
                        \item Purely stacked configuration is missing reflections at 2, 4, 8 and 10 0'clock, but they are there in the parallel displaced conformation
                        \item There is evidence that the stacked configuration will shift towards an offset configuration over time. WAXS spots show up after short simulations, in which case there is visible movement away from a perfectly stacked, towards a parallel displaced conformation
                        \item Pi-stacking reflections are present in all cases but at spacings higher than shown experimentally. This is not surprising since GAFF will not properly treat pi-stacking.
                        \item Interestingly, the spots, which are usually associated with alkyl chain tilt, still appear with an average tilt angle of 0 degrees
                \end{itemize}
                \item Phase B
                \begin{itemize}
                        \item Stacking refelctions present indicating separation of $\approx$ 5 \angstrom
                        \item No spots at all which is consistent with the disorder shown by the rings in the pore
                \end{itemize}
                \item Both phases show a ring in the simulated 2D WAXS patterns at q $\approx$ 1.4 \angstrom \textsuperscript{-1} which is typical of packed alkane chains
                \item Both phases exhibit axial reflections. Even though the rings are not ordered in phase B,
%MRS2: not quite clear what physical structures the axial reflections correspond to (what are the distances? What do they correspond to?)
they are still partitioned into layers which gives rise to an axial refelction at the same distance where we expect alkane chain packing to be present
%MRS2: how are they layers defined here? Can you bring in more information about the nonuniformity of the density?
%BJC2: Are you thinking about the fourier transforms? I could bring that in
        \end{itemize}
